Online Verification of Commutativity

### 2020-09-09 acmPaper/paper.tex
Remove footnote on the first page
Space hacks on the first page
Trim the first page

\newcount\draft\draft=1 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
\documentclass[sigplan,review]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
\usepackage{listings}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Introduction}
\label{introduction}
Many systems can be understood as diagrams: graphs where nodes represent domains and edges represent directed transformation functions between nodes.
A type system with coercions, for example, corresponds to a graph whose nodes are types and whose edges are coercions.
Figure~\ref{fig:typeExample} illustrates an example in a simple language with units-of-measure types.
Such a type system is similar to existing type systems, such as that implemented in F\#~\cite{unitsOfMeasure} and a variety of C-like languages.
In such a system, an important correctness criterion is that the diagram \emph{commutes:} when traversing the graph from any start node to any end node, applying every transformation along the path to any input value, the result is the same output value \emph{independent of the path chosen between the two nodes}.
With our type coercion example, it is a problem if casting to a supposedly equivalent type as an intermediate step resulted in a different answer than a direct cast.
Specifically, given a variable \code{x} of type \code{meters}, applying the cast \code{(wugs) x} can be done in two ways: either \code{(wugs)(feet) x} or \code{(wugs)(miles) x}.
Which path is taken depends on the compiler; we would like the choice of paths to be semantically equivalent so the compiler is free to make a choice.

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \begin{verbatim}
            var a : meters = 1;
            var b : miles = (miles) a;
            var c : feet = (feet) a;
            define wugs:
                1 mile = 10000 wugs;
                1 foot = 10 wugs;
            var d : wugs = (wugs) a;
        \end{verbatim}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}

    \begin{subfigure}{0.4\textwidth}
        \begin{tikzpicture}[scale=0.2]
            \tikzstyle{every node}+=[inner sep=0pt]
            \draw [black] (32.8,-8.8) circle (3);
            \draw (32.8,-8.8) node {$meters$};
            \draw [black] (21.5,-21.4) circle (3);
            \draw (21.5,-21.4) node {$feet$};
            \draw [black] (43.7,-21.4) circle (3);
            \draw (43.7,-21.4) node {$miles$};
            \draw [black] (32.4,-33.6) circle (3);
            \draw (32.4,-33.6) node {$wugs$};
            \draw [black] (30.8,-11.03) -- (23.5,-19.17);
            \fill [black] (23.5,-19.17) -- (24.41,-18.9) -- (23.66,-18.24);
            \draw (26.61,-13.64) node [left] {$\times 3.28$};
            \draw [black] (34.76,-11.07) -- (41.74,-19.13);
            \fill [black] (41.74,-19.13) -- (41.59,-18.2) -- (40.84,-18.85);
            \draw (43.7,-13) node [left] {$\times 6.21 \times 10^{-4}$};
            \draw [black] (23.5,-23.64) -- (30.4,-31.36);
            \fill [black] (30.4,-31.36) -- (30.24,-30.43) -- (29.5,-31.1);
            \draw (26.41,-28.96) node [left] {$\times 10$};
            \draw [black] (41.66,-23.6) -- (34.44,-31.4);
            \fill [black] (34.44,-31.4) -- (35.35,-31.15) -- (34.62,-30.47);
            \draw (37.52,-26.04) node [left] {$\times 10^4$};
            \draw [dashed] (29.441,-34.049) arc (-88.02206:-273.82603:12.915);
            \fill [black] (29.44,-34.05) -- (28.62,-33.58) -- (28.66,-34.58);
            \draw (15.56,-20.93) node [left] {$\times 32.8$};
            \draw [dashed] (35.77,-8.425) arc (90.49177:-92.33986:12.828);
            \fill [black] (35.36,-34.07) -- (36.13,-34.6) -- (36.18,-33.6);
            \draw (49.23,-21.46) node [right] {$\times 6.21$};
            \end{tikzpicture}
        \caption{Diagram for the type conversions in the program}
    \end{subfigure}

    \caption{In this sample program, the user implicitly defines two ways to cast variable a from meters to the new unit wugs.
    The definitions are different, and a compiler performing implicit conversion would not know which to choose.}
    \label{fig:typeExample}
\end{figure}

>>>>

\newcount\draft\draft=1 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
\documentclass[sigplan,review,nonacm=true]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
\usepackage{listings}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Introduction}
\label{introduction}
Many systems use diagrams: graphs where nodes are domains and edges are transformation functions.
A type system with coercions, for example, corresponds to a graph whose nodes are types and whose edges are coercions.
Figure~\ref{fig:typeExample} illustrates an example in a simple language with units-of-measure types~\cite{unitsOfMeasure}.
In such a system, an important correctness criterion is that the diagram \emph{commutes:} when traversing the graph from any start node to any end node, applying every transformation along the path to any input value, the result is the same output value \emph{independent of the path chosen between the two nodes}.
With our coercion example, it is a problem if casting to a supposedly equivalent type as an intermediate step resulted in a different answer than a direct cast.
Specifically, given a variable \code{x} of type \code{meters}, applying the cast \code{(wugs) x} can be done in two ways: either \code{(wugs)(feet) x} or \code{(wugs)(miles) x}.
Which path is taken depends on the compiler; we would like the choice of paths to be semantically equivalent so the compiler is free to make a choice.

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \begin{verbatim}
            var a : meters = 1;
            var b : miles = (miles) a;
            var c : feet = (feet) a;
            define wugs:
                1 mile = 10000 wugs;
                1 foot = 10 wugs;
            var d : wugs = (wugs) a;
        \end{verbatim}
        \vspace{-3ex}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}

    \begin{subfigure}{0.4\textwidth}
        \begin{tikzpicture}[scale=0.2]
            \tikzstyle{every node}+=[inner sep=0pt]
            \draw [black] (32.8,-8.8) circle (3);
            \draw (32.8,-8.8) node {$meters$};
            \draw [black] (21.5,-21.4) circle (3);
            \draw (21.5,-21.4) node {$feet$};
            \draw [black] (43.7,-21.4) circle (3);
            \draw (43.7,-21.4) node {$miles$};
            \draw [black] (32.4,-33.6) circle (3);
            \draw (32.4,-33.6) node {$wugs$};
            \draw [black] (30.8,-11.03) -- (23.5,-19.17);
            \fill [black] (23.5,-19.17) -- (24.41,-18.9) -- (23.66,-18.24);
            \draw (26.61,-13.64) node [left] {$\times 3.28$};
            \draw [black] (34.76,-11.07) -- (41.74,-19.13);
            \fill [black] (41.74,-19.13) -- (41.59,-18.2) -- (40.84,-18.85);
            \draw (43.7,-13) node [left] {$\times 6.21 \times 10^{-4}$};
            \draw [black] (23.5,-23.64) -- (30.4,-31.36);
            \fill [black] (30.4,-31.36) -- (30.24,-30.43) -- (29.5,-31.1);
            \draw (26.41,-28.96) node [left] {$\times 10$};
            \draw [black] (41.66,-23.6) -- (34.44,-31.4);
            \fill [black] (34.44,-31.4) -- (35.35,-31.15) -- (34.62,-30.47);
            \draw (37.52,-26.04) node [left] {$\times 10^4$};
            \draw [dashed] (29.441,-34.049) arc (-88.02206:-273.82603:12.915);
            \fill [black] (29.44,-34.05) -- (28.62,-33.58) -- (28.66,-34.58);
            \draw (15.56,-20.93) node [left] {$\times 32.8$};
            \draw [dashed] (35.77,-8.425) arc (90.49177:-92.33986:12.828);
            \fill [black] (35.36,-34.07) -- (36.13,-34.6) -- (36.18,-33.6);
            \draw (49.23,-21.46) node [right] {$\times 6.21$};
            \end{tikzpicture}
        \caption{Diagram for the type conversions in the program}
    \end{subfigure}
    \vspace{-2ex}
    \caption{In this sample program, the user implicitly defines two ways to cast variable a from meters to the new unit wugs.
    The definitions are different, and a compiler performing implicit conversion would not know which to choose.}
    \label{fig:typeExample}
\end{figure}
